F1000 paper figures

### 2017-06-19 inst/paper/figs.Rmd
grey scale colors and add lines per expression

---
title: "F1000 paper figures"
author: "Kent Riemondy RBI"
date: "June 6, 2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(cache = TRUE)
```

@@

plot_a <- ggplot(res, aes(x=reorder(expr, time), y = time)) +
  geom_boxplot(width = 0.75, size = 0.33, outlier.shape = NA, fill = RColorBrewer::brewer.pal(3, "Set1")[2]) +
  coord_flip() +
  theme_bw() +
  labs(
    y='execution time (seconds)',
    x='',
    subtitle=paste0(comma(n), " random x/y intervals,\n", comma(nrep), " repetitions")) +
  theme_classic() +
  pub_theme +
  theme(
    legend.text = element_text(size = 14),
    legend.title = element_blank(),
    legend.position = "none",
    plot.subtitle = element_text(size = 18),
    axis.text.x = element_text(angle = 90)
  )

plot_b <- ggplot(dat, aes(x=reorder(func, time), y = time, fill = package)) +
  geom_boxplot(width = 0.75, size = 0.33, outlier.shape = NA) +
  scale_fill_brewer(palette = "Set1") + 
  coord_flip() +
  theme_bw() +
  labs(
    y='execution time (seconds)',
    x='') +
  theme_classic() +
  pub_theme +
  theme(
    legend.text = element_text(size = 18),
    legend.title = element_blank(),
    legend.position = "top",
    axis.text.x = element_text(angle = 90)
  )

@@

Here we examine the overlap of repeat classes in the human genome (on `chr22` only, for simplicity) using `bed_jaccard()`.

```{r reldist_shuffle, message = FALSE, warning = FALSE}

repeats <- read_bed(valr_example('hg19.rmsk.chr22.bed.gz'), n_fields = 6) 
genome <- read_genome(valr_example('hg19.chrom.sizes.gz'))
genes <- read_bed12(valr_example('hg19.refGene.chr22.bed.gz'))
exons <- bed12_to_exons(genes)

shuffle_intervals <- function(n, .data, genome) {
  replicate(n, bed_shuffle(.data, genome), simplify = FALSE) %>%
    bind_rows(.id = 'rep') %>%
    group_by(rep) %>% nest()
}

shuffled <- shuffle_intervals(n = 100, repeats, genome) %>%
  mutate(jaccard = data %>%
           map(bed_jaccard, repeats) %>%
           map_dbl("jaccard"))

shuffled

bed_jaccard(repeats, exons)
```

>>>>

---
title: "F1000 paper figures"
author: "Kent Riemondy RBI"
date: "June 6, 2017"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set( 
  collapse = TRUE,
  comment = "#>",
  cache = TRUE,
  echo = TRUE)
```

@@

plot_a <- ggplot(res, aes(x=reorder(expr, time), y = time)) +
  geom_boxplot(width = 0.75, size = 0.33, outlier.shape = NA, fill = grDevices::grey.colors(2)[2]) +
  coord_flip() +
  theme_bw() +
  labs(
    y='execution time (seconds)',
    x='',
    subtitle=paste0(comma(n), " random x/y intervals,\n", comma(nrep), " repetitions")) +
  theme_classic() +
  pub_theme +
  theme(
    legend.text = element_text(size = 14),
    legend.title = element_blank(),
    legend.position = "none",
    plot.subtitle = element_text(size = 18),
    axis.text.x = element_text(angle = 90)
  )

plot_b <- ggplot(dat, aes(x=reorder(func, time), y = time, fill = package)) +
  geom_boxplot(width = 0.75, size = 0.33, outlier.shape = NA) +
  scale_fill_grey() + 
  coord_flip() +
  geom_vline(xintercept = seq_along(unique(dat$func)) + 0.5,
             color = "grey") +
  theme_bw() +
  labs(
    y='execution time (seconds)',
    x='') +
  theme_classic() +
  pub_theme +
  theme(
    legend.text = element_text(size = 18),
    legend.title = element_blank(),
    legend.position = "top",
    axis.text.x = element_text(angle = 90)
  )

@@

Here we examine the extent of overlap of repeat classes with exons in the human genome (on `chr22` only, for simplicity) using the jaccard similarity index. `bed_jaccard()` implements the jaccard test to examine the similarity between two sets of genomic intervals. Using `bed_shuffle()` and `replicate()` we generate a `data_frame` containing 100 sets of randomly placed intervals then calculate the jaccard index for each set to generate a null-distribution of jaccard scores. Finally an empirical p-value is then calculated from the null-distribution.

```{r reldist_shuffle, message = FALSE, warning = FALSE}
library(tidyverse, warn.conflicts = F)

repeats <- read_bed(valr_example('hg19.rmsk.chr22.bed.gz'), n_fields = 6) 
genome <- read_genome(valr_example('hg19.chrom.sizes.gz'))
genes <- read_bed12(valr_example('hg19.refGene.chr22.bed.gz'))
# convert bed12 to bed with exons
exons <- bed12_to_exons(genes)

# function to repeat interval shuffling
shuffle_intervals <- function(n, .data, genome) {
  replicate(n, bed_shuffle(.data, genome), simplify = FALSE) %>%
    bind_rows(.id = 'rep') %>%
    group_by(rep) %>% nest()
}
nreps <- 100
shuffled <- shuffle_intervals(n = nreps, repeats, genome) %>%
  mutate(jaccard = data %>%
           map(bed_jaccard, repeats) %>%
           map_dbl("jaccard"))
shuffled

obs <- bed_jaccard(repeats, exons)
obs

pvalue <- sum(shuffled$jaccard >= obs$jaccard) + 1 /(nreps + 1)
pvalue
```
